Convert

### 2024-06-13 qmd/projects/msu/wss/convert.Rmd
update

```{r convert2}
# create a word document version of this document
# first need to copy and paste all of the content from this 
# document into an .RMD file so that I can convert the .RMD
# into a word document
library(rmarkdown)
content <- readLines("paper1.qmd", warn = FALSE)
writeLines(content, "paper1.rmd")
render("paper1.rmd", 
       output_format = "word_document",
       output_file = paste0("JacksonStrand_Paper 1.docx"))
render("paper1.rmd", output_format = "pdf_document",
       output_file = paste0("JacksonStrand_Paper 1.pdf"))

>>>>

```{r convert2}
# create a word document version of this document
# first need to copy and paste all of the content from this 
# document into an .RMD file so that I can convert the .RMD
# into a word document
library(rmarkdown)
content <- readLines("paper_1.qmd", warn = FALSE)
writeLines(content, "paper1.rmd")
render("paper1.rmd", 
       output_format = "word_document",
       output_file = paste0("JacksonStrand_Paper 1.docx"))
# render("paper1.rmd", output_format = "pdf_document",
#        output_file = paste0("JacksonStrand_Paper 1.pdf"))
